shrimp_goby_boatnoise

### 2025-03-05 ms_boatnoise_shrimp_goby.Rmd
addressing Jake Martin's comments with addition of temporary code for explination

```{r}
#posterior predictive checks
pp_check(goby_out_model, ndraws = 50)

@@

@@

>>>>

```{r}
pp_check(goby_out_model, ndraws = 50)

@@

```{r}
loo(shrimp_out_model)
```

@@

#Delete me I am one of Jack's rabbit holes

```{r}
priors <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "coi"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "zoi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "coi", lb = 0),
            set_prior("normal(0, 3)", class = "b"),
            set_prior("normal(0, 3)", class = "b", dpar = "phi"),
            set_prior("normal(0, 3)", class = "b", dpar = "zoi"),
            set_prior("normal(0, 3)", class = "b", dpar = "coi"))

priors1 <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "zoi", lb = 0),
            set_prior("normal(0, 3)", class = "b"),
            set_prior("normal(0, 3)", class = "b", dpar = "phi"),
            set_prior("normal(0, 3)", class = "b", dpar = "zoi"))

priors2 <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
            set_prior("normal(0, 3)", class = "b"))

priors3 <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "coi"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
            set_prior("normal(0, 3)", class = "b"),
            set_prior("normal(0, 3)", class = "b", dpar = "phi"),
            set_prior("normal(0, 3)", class = "b", dpar = "zoi"),
            set_prior("normal(0, 3)", class = "b", dpar = "coi"))

priors4 <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
            set_prior("normal(0, 3)", class = "b"))
```

```{r}
goby_out_formula_simple1 <- bf(
  # mu (mean) part
  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # phi (precision) part
  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # alpha (zero-one-inflation) part
  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # The one-inflated part, conditional on the 0s
  coi ~ 1,

goby_out_model_simple1 <- brm(
  goby_out_formula_simple1,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors1,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 1
)
```

```{r}
goby_out_formula_simple2 <- bf(
  # mu (mean) part
  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # phi (precision) part
  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
  # alpha (zero-one-inflation) part
  zoi ~ 1,
  # The one-inflated part, conditional on the 0s
  coi ~ 1,

goby_out_model_simple2 <- brm(
  goby_out_formula_simple2,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors2,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 1
)
```

```{r}
goby_out_formula_simple3 <- bf(
  # mu (mean) part
  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species + (1 | site/burrow),
  # phi (precision) part
  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
  # alpha (zero-one-inflation) part
  zoi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
  # The one-inflated part, conditional on the 0s
  coi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,

goby_out_model_simple3 <- brm(
  goby_out_formula_simple3,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors3,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 1
)
```

```{r}
goby_out_formula_simple4 <- bf(
  # mu (mean) part
  goby_out ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
  # phi (precision) part
  phi ~ stroke*stage + goby_number + shrimp_number + shrimp_species,
  # alpha (zero-one-inflation) part
  zoi ~ 1,
  # The one-inflated part, conditional on the 0s
  coi ~ 1,

goby_out_model_simple4 <- brm(
  goby_out_formula_simple4,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors4,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 1
)
```

```{r}
pp_check(goby_out_model, ndraws = 50)
pp_check(goby_out_model_simple1, ndraws = 50)
pp_check(goby_out_model_simple2, ndraws = 50)
pp_check(goby_out_model_simple3, ndraws = 50)
pp_check(goby_out_model_simple4, ndraws = 50)
pp_check(goby_out_model, type='stat', stat='mean')
pp_check(goby_out_model_simple1, type='stat', stat='mean')
pp_check(goby_out_model_simple2, type='stat', stat='mean')
pp_check(goby_out_model_simple3, type='stat', stat='mean')
pp_check(goby_out_model_simple4, type='stat', stat='mean')
```

```{r}
loo(goby_out_model_simple1)
```

```{r}
loo(goby_out_model_simple2)
```

```{r}
loo(goby_out_model_simple3)
```

```{r}
loo(goby_out_model_simple4)
```
